Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-27 paper/paper.Rmd
make forecast visualisation more naunced #14

```{r vis-forecasts, fig.cap = "a.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom. b.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_wis(wis, locs) +
   theme(strip.text.x = element_blank()) |
  plot_forecasts(forecasts, locs, ranges) +
    guides(fill = guide_none(), fill_ramp = guide_none(), col = guide_none())
) +
  plot_layout(widths = c(1, 4), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

>>>>

```{r vis-forecasts, fig.cap = a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.
b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```
